Devphotodraw_main_anlayses

### 2021-06-24 analysis/step6_main_analyses/devphotodraw_main_analysis.Rmd
add rmarkdown manuscript file to repo

humans_merged <- humans %>%
  group_by(unique_ids, category) %>% # group by each drawing of each category
  summarize(num_correct = mean(correct_or_not)) %>%
  left_join(d, by=c('unique_ids','category')) %>% # join with classification data 
  filter(!is.na(age))
```

@@

## Main descriptive anlayses 
### Compute accuracy by age, condition, site 
```{r descriptives-across-age}
cor_by_age_by_site_by_cond <- d %>%  
  group_by(unique_ids,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") %>%
  mutate(who = "model")

@@

### Plot accuracy by age, condition, site 
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(humans_and_models, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(who~site)
```
### Compute effort/tracing by age, condition, site 
```{r}
draw_duration <- d %>%
  group_by(unique_ids,condition,age_numeric, site) %>%
  summarize(avg_draw_duration = mean(draw_duration)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_draw_duration")

@@

>>>>

humans_merged <- humans %>%
  group_by(unique_ids, category, image_name_short) %>% # group by each drawing of each category
  summarize(num_correct = mean(correct_or_not)) %>%
  left_join(d, by=c('unique_ids','category')) %>% # join with classification data 
  filter(!is.na(age))
```

@@

```{r}

category_age_cond <- humans_merged %>%
  group_by(category, condition) %>%
  summarize(humans_pc = mean(num_correct), model_pc = mean(correct_or_not, na.rm=TRUE))

```{r}
ggplot(category_age_cond, aes(x=model_pc, y=humans_pc, color=condition))+
  geom_point() +
  ylim(0,1) +
  xlim(0,1) +
  theme_few() +
  theme(aspect.ratio = 1) +
  facet_wrap(~category) +
  geom_abline(color='grey')

```
```{r}
ggplot(category_age_cond, aes(x=model_pc, y=humans_pc, label=category))+
  geom_point() +
  ylim(0,1) +
  xlim(0,1) +
  theme_few() +
  theme(aspect.ratio = 1) +
  facet_wrap(~condition) +
  geom_abline(xintercept=0, color='grey') +
  ggrepel::geom_label_repel() 
```
## Main descriptive anlayses 
### Compute accuracy by age, condition, site 
```{r descriptives-across-age}
cor_by_age_by_site_by_cond <- d %>%  
  group_by(unique_ids,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") %>%
  mutate(who = "model")

@@

```{r descriptives-across-age}
cor_by_age_by_cond <- d %>%  
  group_by(unique_ids,category,condition,age_numeric) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,condition) %>%
  multi_boot_standard(col = "avg_cor") %>%
  mutate(who = "model")

cor_by_age_by_cond_humans <- humans_merged %>%  
  group_by(unique_ids,category,condition,age_numeric) %>%
  summarize(avg_cor = mean(num_correct)) %>%
  group_by(age_numeric,condition) %>%
  multi_boot_standard(col = "avg_cor") %>%
  mutate(who = 'humans')

humans_and_models_no_site <- cor_by_age_by_cond_humans %>%
  full_join(cor_by_age_by_cond)
```

### Plot accuracy by age, condition, site 
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(humans_and_models, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(who~site)
```
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(humans_and_models_no_site, aes(age_numeric,mean, col = conditionf)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(~who)

```
```{r}
disagreements <- humans_merged %>%
  filter(num_correct>.8) %>%
  filter(correct_or_not==0) %>%
  filter(condition=='S')

disagreements <- disagreements %>%
  mutate(image_path = here::here('data/compiled/drawings/object_drawings', image_name_short)) %>%
  mutate(new_image_path = here::here('data/compiled/drawings/disagreements', image_name_short))

dir.create(here::here('data/compiled/drawings/disagreements'))

file.copy(disagreements$image_path, disagreements$new_image_path)

```{r}
machine_p_advantage <- humans_merged %>%
  filter(num_correct<.5) %>%
  filter(correct_or_not==1) %>%
  filter(condition=='P')

machine_p_advantage <- machine_p_advantage %>%
  mutate(image_path = here::here('data/compiled/drawings/object_drawings', image_name_short)) %>%
  mutate(new_image_path = here::here('data/compiled/drawings/machine_p_advantage', image_name_short))

dir.create(here::here('data/compiled/drawings/machine_p_advantage'))

file.copy(machine_p_advantage$image_path, machine_p_advantage$new_image_path)

### Compute effort/tracing by age, condition, site 
```{r}
draw_duration <- d %>%
  group_by(unique_ids,condition,age_numeric, site) %>%
  summarize(avg_draw_duration = mean(draw_duration)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_draw_duration")

@@

```{r}
item_effects <- humans_merged %>%
  group_by(session_id,age_numeric,category, site) %>%
  summarize(avg_sub_cor = mean(num_correct)) %>%
  group_by(age_numeric,category, site) %>%
  summarize(avg_cor = mean(avg_sub_cor)) %>%
  spread(key=site, value=avg_cor)

ggplot(item_effects, aes(x=CDM, y=THU, color=age_numeric)) +
  geom_point() + 
  theme_few(base_size = base_size_chosen) + 
  ylim(0,1) + 
  xlim(0,1) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  geom_abline(color = 'grey', intercept=0) + 
  facet_wrap(~category)
```

```{r}
item_effects_not_spread <- humans_merged %>%
  group_by(session_id,age_numeric,category, site) %>%
  summarize(avg_sub_cor = mean(num_correct)) %>%
  group_by(age_numeric,category, site) %>%
  multi_boot_standard(col = "avg_sub_cor")

ggplot(item_effects_not_spread, aes(x=as.numeric(age_numeric), y=mean, color=site)) +
  geom_point() +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  ylim(0,1) + 
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  ylab('Proportion correct') +
  xlab('Age (in years)') +
  geom_abline(color = 'grey', intercept=0) +
  geom_smooth(span=20, alpha=.1) +
  facet_wrap(~category)
```

```{r}
item_effects <- humans_merged %>%
  group_by(age_numeric,category) %>%
  summarize(model_pc = mean(correct_or_not), human_pc = mean(num_correct))

ggplot(item_effects, aes(x=model_pc, y=human_pc, color=age_numeric)) +
  geom_point() + 
  theme_few(base_size = base_size_chosen) + 
  ylim(0,1) + 
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_wrap(~category)
```
